Clustering of Last.fm Music Artists

### 2015-05-03 MSDgroupwriteup.tex
more discussion

The full matrix was originally $163206$ users x $110000$ songs.

@@

How to split into training and test? 
Random selection by user or element?
Need matrixes to be the same size to compare them.

Interesting plots:
- Cumulative Distribution of number of songs with a given play count
-

>>>>

The full matrix was originally $163206$ songs x $110000$ users.

@@

SONG PLAY COUNT  \\
mean = 28 \\
max = 35432 \\
std = 215.826789\\

USER PLAY COUNT\\
mean = 42\\
max = 1305\\
min = 5\\
std = 53.31547\\

How to split into training and test? 
Random selection by user or element? ELEMENT. 
Need matrixes to be the same size to compare them.

Interesting plots:
- Cumulative Distribution of number of songs with a given play count
